---
title: "WUP_03"
author: "Claryssa Jimenez"
date: "2024-02-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tigerstats)
library(tidyverse)
data (ucdavis1)
davisdata = ucdavis1
```

# Introduction 

The research question is: Is there a difference in the average amount of alcohol consumed per week by UC Davis Students based on the different rows they sit in class?

$H_0$: There is no difference between the average number of drinks imbibed between people based on the row they sit in.

$H_A$: The average number drinks is different between at least two rows.   

# Methods

Data from UC Davis: Seat is categorical; alcohol is  numerical. 
Therefore we will use the Numerical~Categorical helper file. 

# Description 

### Graphical Description

```{r}
boxplot(alcohol~Seat,data=ucdavis1)
```

This boxplot shows that the students in the back row tend to drink more than the other 2 rows. 

### Numerical Description

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The numerical description of this table shows the median Back Seat consumption is 3.5, Front Seat consumption is 0.0, and Middle Seat consumption is 1.0


### Inferential Results 

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The inferential results show that: 

The p-value is 0.000353 which is < 0.5, meaning that there is not a difference in the amount of alcohol consumption.  


### When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```

The HSD plot is showing that the students seat in the back row consume significantly more alcohol that the students in the front and middle rows. 










