---
title: "Alcohol vs Seat choice"
author: "Claryssa Jimenez"
date: "Feb 5 2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question: Is there a difference between the alcohol consumed between the row you choose to sit in??

# Introduction

Data are from the UCDavis.csv

Is the average amount of alcohol consumed per week different for the different seating rows?

$H_0$: There is NO difference in the average amount of alcohol consumed per week based on different seating rows. 

$H_A$ There is a difference in the average amount of alcohol consumed per week based on different seating rows. 


# Methods

We are trying to predict the alcohol consumption per week based on the seat row they are sat in. alcohol~Seat

Alcohol is a numerical variable. Seat is categorical variable, therefore we use the num~cat helper file. 


## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
```{r}
boxplot(alcohol~Seat,data=davisdata)
```
  
This boxplot shows the difference in the number of alcohol consumed in the back, front, and middle seats. 
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

## Inferential Tests

## Conclusions


